\documentclass{ximera}

\input{../../preamble.tex}

\title[Summary]{Summary}

\begin{document}
\begin{abstract} \end{abstract}
\maketitle

\textbf{What we need to know about functions}
\begin{itemize}
	\item State the definition of a function.
	\item Find the domain and range of a function.
	\item Distinguish between functions by considering their domains.
	\item Recognize different representations of the same function.
	\item Determine where a function is positive or negative.
	\item Determine algebraically whether a function is even, odd, or neither.
	\item Use symmetry  when  graphing  even or odd functions.
	\item Plot basic functions.
	\item Apply appropriate transformations to graphs of basic functions\\
	         (vertical and horizontal shifts, vertical and horizontal stretching and reflecting)
        \item Perform basic operations and compositions on functions.
        \item Work with piecewise defined functions.
	\item Determine if a function is one-to-one.
        \item Define and work with inverse functions.
        \item Plot inverses of basic functions.
	\item Find inverse functions (algebraically and graphically).
        \item Find the largest interval containing a given point
          where the function is invertible.
	\item Determine the intervals on which a function has an inverse.
         \item Relate the domain and range of $f$ and the domain and range of $f^{-1}$.  
	\item Use a sign-chart to determine where the function is positive/negative.
\end{itemize}





\end{document}
