\documentclass{ximera}

\input{../preamble.tex}


\title[Problem 11]{Problem 11}

\begin{document}
\begin{abstract} \end{abstract}
\maketitle


% Extracted from usingLimitsToDetectAsymptotes.tex, problem #11
\begin{problem}

  For the function $g$ defined by 
  \[
    g(t) = \frac{t^2 + 7t + 11}{t-3}
  \]
  \begin{enumerate}
    \item
      Find all vertical asymptotes.   \textbf{EXPLAIN} and justify your answer by using appropriate limits.
\begin{explanation}
         The function $g$ is a rational function which is continuous on the intervals $(-\infty, 3)$ and $(3, \infty)$. 	
         The only candidates for a vertical asymptote is $t = 3$, where $g$ is not defined.

        Test of candidate $t = 3$:
        \begin{align*}
          &\lim_{t \to 3^+} \frac{t^2 + 7t + 11}{t-3}= \infty \\
             \end{align*}
	Note: the limit is of the form $ \frac{\#}{0}$, the numerator positive, and the denominator also positive.  \\
      The line $t=3$ is a vertical asymptote of $g$ since $\lim_{t\to 3^+} g(t) = \infty$.
     


      \end{explanation}


    \item

      Find all horizontal asymptotes. \textbf{EXPLAIN} and justify your answer by using appropriate limits.
\begin{explanation}
	To find the limits, we need to divide the numerator and denominator by the highest power of $t$ in the denominator.
        \begin{align*} 
         &\lim_{t \to \infty} \frac{t^2 + 7t + 11}{t-3} = \lim_{t \to \infty} \frac{t + 7 + \frac{11}{t}}{1-\frac{3}{t}} = \infty \\
            \end{align*}
	Note:  the last limit is of the form $ \frac{\infty}{\#}$, the numerator positive, the denominator  positive. \\

        Therefore, $g$ has no horizontal asymptotes as $ t \to \infty$.
     

        \begin{align*} 
         &\lim_{t \to -\infty} \frac{t^2 + 7t + 11}{t-3} = \lim_{t \to- \infty} \frac{t +7 + \frac{11}{t}}{1-\frac{3}{t}} = -\infty \\
            \end{align*}
	Note:  the last limit is of the form $ \frac{\infty}{\#}$, the numerator negative, the denominator positive.  \\
	
        Therefore, $g$ has no horizontal asymptotes as $ t \to -\infty$ either.
     

      \end{explanation}
  \end{enumerate}
\end{problem}



\end{document}
