\documentclass{ximera}

\input{../preamble.tex}


\title[Problem 4]{Problem 4}

\begin{document}
\begin{abstract} \end{abstract}
\maketitle

 % for drawing cube in Optimization problem
\usetikzlibrary{quotes,arrows.meta}
\tikzset{
  annotated cuboid/.pic={
    \tikzset{%
      every edge quotes/.append style={midway, auto},
      /cuboid/.cd,
      #1
    }
    \draw [every edge/.append style={pic actions, densely dashed, opacity=.5}, pic actions]
    (0,0,0) coordinate (o) -- ++(-\cubescale*\cubex,0,0) coordinate (a) -- ++(0,-\cubescale*\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubescale*\cubez)  -- ++(\cubescale*\cubex,0,0) coordinate (c) -- cycle
    (o) -- ++(0,0,-\cubescale*\cubez) coordinate (d) -- ++(0,-\cubescale*\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
    (o) -- (a) -- ++(0,0,-\cubescale*\cubez) coordinate (f) edge (g) -- (d) -- cycle;
    \path [every edge/.append style={pic actions, |-|}]
    (b) +(0,-5pt) coordinate (b1) edge ["y"'] (b1 -| c)
    (b) +(-5pt,0) coordinate (b2) edge ["x"] (b2 |- a)
    (c) +(3.5pt,-3.5pt) coordinate (c2) edge ["x"'] ([xshift=3.5pt,yshift=-3.5pt]e)
    ;
  },
  /cuboid/.search also={/tikz},
  /cuboid/.cd,
  width/.store in=\cubex,
  height/.store in=\cubey,
  depth/.store in=\cubez,
  units/.store in=\cubeunits,
  scale/.store in=\cubescale,
  width=10,
  height=10,
  depth=10,
  units=cm,
  scale=.1,
}

% Extracted from optimization.tex, problem #4
\begin{problem}
A box with two square sides is constructed to have a volume of 27. Denote the dimensions of the length of the base as $y$, and the width and height as $x$, as labeled in the diagram below. Find the dimensions needed to minimize the surface area of the box.
		\begin{center}
		\begin{tikzpicture}
			\pic {annotated cuboid={width=120, height=95, depth=95, scale=.02, units=cm}};
		\end{tikzpicture}
		\end{center}
		Solve the problem by performing the following steps.

		
		\begin{enumerate}
			\item Find a formula for $S(x)$ the surface area of the box, as a function of only the variable $x$.
 
 	\begin{explanation}
        				The volume of the box is given by $V=x^2 y$ and the surface area is given by $S = 2x^2 + 4xy$. We are told that the volume of the box is 27, which means our constraint is that $x^2y = 27$, so that $y = \frac{27}{x^2}$. Plugging this into the surface area formula gives 
        				\[ S(x) = 2x^2 + 4x\left( \frac{27}{x^2} \right) = 2x^2 + \frac{108}{x} \]
			      \end{explanation}
			\item Find the{interval of interest} for $S(x)$. 
\begin{explanation}
        				Because $x$ represents a side-length of this box, it cannot be negative. Moreover, the function $S(x)$ is not defined at $x=0$,
        				so $x$ has to be positive. The Interval of Interest is $(0,\infty)$.
			      \end{explanation}
			      
			\item Find the $x$-value that gives the minimum surface area over all 
				such boxes.
[2]
				\begin{explanation}
        				Our objective function $S(x) = 2x^2 + \frac{108}{x}$ is continuous on the open interval $(0,\infty)$. This domain is an 
        				open interval, so to find the global minimum we start by finding the local extrema.
        				
        				$S'(x) = 4x - \frac{108}{x^2}$. This exists for all nonzero values of $x$, and since $x=0$ is not in our interval of interest,
        				our critical points must have $S'(x)=0$.
        				\begin{align*}
        					S'(x) &= 0\\
        					4x - \frac{108}{x^2} &= 0\\
						4x &= \frac{108}{x^2}\\
						x^3 &= 27\\
						x &= 3.
        				\end{align*} 
        				
        				There is one critical point, at $x=3$. Since $S''(x) = 4 + \frac{216}{x^3}$, we have $S''(3) = 4 + \frac{216}{27} > 0$. By the
        				Second Derivative Test, $x=3$ is a local minimum.
        				
        				Since $x=3$ was the only local extremum on the open interval $(0,\infty)$, it is the global minimum as well.
			      \end{explanation}
			      
	\end{enumerate}	

\end{problem}



\end{document}
